|

### 2022-12-25 rmd/supporting_info.Rmd
Update supporting_info.Rmd

```{=tex}
\newpage
\pagestyle{fancy}
\fancyhead[L]{Terui et al.}
\fancyhead[C]{}
\pagenumbering{arabic}
\def\figurename{Figure S\hspace{-.4ex}}
\def\tablename{Table S\hspace{-.4ex}}
```
# Supplementary Text

@@

```{r fig-env, fig.width=11, fig.height=8, fig.cap="Distribution of environmental variables in the protected watershed. Note that the number of fish released and ocean productivity (chlorophyll a) are measured at the watershed level while others are measured at the site level."}

>>>>

```{=tex}
\newpage
\pagestyle{fancy}
\fancyhead[L]{Terui et al.}
\fancyhead[C]{}
\renewcommand{\headrulewidth}{0.5pt}
\pagenumbering{arabic}
\def\figurename{Figure S\hspace{-.4ex}}
\def\tablename{Table S\hspace{-.4ex}}
```
# Supplementary Text

@@

```{r fig-env, fig.width=11, fig.height=8, fig.cap="Distribution of environmental variables in the protected watershed. Note that the number of fish released, ocean productivity (chlorophyll a), and SD elevation are measured at the watershed level while others are measured at the site level."}
